Field training 02 - Leaf traits measurements

### 2023-06-13 submission_2/submission_2.qmd
Adds authors, fixes order and naming

---
title: "Field training 02 - Leaf traits measurements"
subtitle: "Documentation"
subsubtitle: "Leaf traits measurements"
author: "Denis Streitmatter"
date: last-modified
format:
    pdf:
        documentclass: scrreport
        theme: united
        toc: true
        toc-depth: 2
        number-sections: true
        number-depth: 1
        toc-title: Table of Contents
        toc-location: body
        colorlinks: true
header-includes:  
- \usepackage{graphicx}
- \usepackage{lscape}
- \usepackage{array}
---

@@

# Leaf Properties Sampling

# Task 1: Procedure

@@

Group-ID: 4

Participants: Dennis, Fabian, Louis, Lukas, Marie-Louise, Maxwell

@@

## Leaf water content

<!-- change back to portrait -->
\KOMAoptions{paper=portrait,pagesize} 
\recalctypearea

- Smartphone (GPS + plant species determination)
- Book (Flora Vegetativa)
- Survey sheet

@@

## Leaf images

## Recorded species tables

<!--
Table in landscape format (uncomment if needed)

# landscape table format (better?)

::::::::{.landscape data-latex=""}

\begin{table}[]
\fontsize{22}{\baselineskip}\selectfont
\renewcommand{\arraystretch}{4}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
\textbf{Group-ID} &
  \textbf{Plot-ID} &
  \textbf{Subplot-ID} &
  \textbf{Date} &
  \textbf{\begin{tabular}[c]{@{}c@{}}X-Coordinate \\ center\end{tabular}} &
  \textbf{\begin{tabular}[c]{@{}c@{}}Y-Coordinate \\ center\end{tabular}} &
  \textbf{Litter / \%} &
  \textbf{Soil / \%} &
  \textbf{Water / \%} &
  \textbf{Moss / \%} &
  \textbf{Height / cm} &
  \textbf{\begin{tabular}[c]{@{}c@{}}Acer \\ platanoides\end{tabular}} &
  \textbf{\begin{tabular}[c]{@{}c@{}}Achillea \\ millefolium\end{tabular}} &
  \textbf{\begin{tabular}[c]{@{}c@{}}Bellis \\ perennis\end{tabular}} &
  \textbf{\begin{tabular}[c]{@{}c@{}}Capsella \\ bursa-pastoris\end{tabular}} &
  \textbf{\begin{tabular}[c]{@{}c@{}}Dactylis \\ glomerata\end{tabular}} &
  \textbf{\begin{tabular}[c]{@{}c@{}}Elymus \\ repens\end{tabular}} &
  \textbf{\begin{tabular}[c]{@{}c@{}}Geranium \\ molle\end{tabular}} &
  \textbf{\begin{tabular}[c]{@{}c@{}}Geranium \\ pusillum\end{tabular}} &
  \textbf{\begin{tabular}[c]{@{}c@{}}Lolium \\ perenne\end{tabular}} &
  \textbf{\begin{tabular}[c]{@{}c@{}}Poa \\ annua\end{tabular}} &
  \textbf{\begin{tabular}[c]{@{}c@{}}Polygonum \\ aviculare\end{tabular}} &
  \textbf{\begin{tabular}[c]{@{}c@{}}Trifolium \\ repens\end{tabular}} &
  \textbf{\begin{tabular}[c]{@{}c@{}}Veronica \\ arvensis\end{tabular}} \\ \hline
4 & 1 & 1 & 16.05.2023 & 51.332222 & 12.384167 & 1.5 & 11 & 0 & 8 & 6 &     &     & 15 & 4 &   & 2  & 15 & 1 & 50 & 10 & 0.5 & 10 & 1   \\ \hline
4 & 1 & 2 & 16.05.2023 &           &           & 1   & 4  & 0 & 1 & 6 &     & 0.5 & 22 &   & 2 &    & 18 & 1 & 55 & 15 & 0.5 &    & 1   \\ \hline
4 & 1 & 3 & 16.05.2023 &           &           & 1   & 3  & 0 & 2 & 6 & 0.5 & 3   & 8  &   &   & 1  & 19 &   & 38 & 19 &     & 18 & 0.5 \\ \hline
4 & 1 & 4 & 16.05.2023 &           &           & 1   & 10 & 0 & 1 & 4 &     &     & 6  &   &   & 15 & 17 &   & 28 & 10 & 0.5 & 1  & 2   \\ \hline
\end{tabular}%
}
\caption{Subplot x species table for the recorded herbaceous vegetation. The values are the cover fraction of the total plot in {[}\%{]}.}
\end{table}
::::::::

-->

@@

>>>>

---
title: "Field training 02 - Leaf traits measurements"
subtitle: "Documentation"
subsubtitle: "Leaf traits measurements"
author: 
    - "Group 4" 
    - "Denis Streitmatter"
    - "Marie-Louise Korte"
    - "Louis Trinkle"
    - "Maxwell Sivertsen"
    - "Fabian Götz"
    - "Lukas Erzfeld"
date: last-modified
format:
    pdf:
        documentclass: scrreport
        theme: united
        toc: true
        toc-depth: 2
        number-sections: false 
        number-depth: 1
        toc-title: Table of Contents
        toc-location: body
        colorlinks: true
header-includes:  
- \usepackage{graphicx}
- \usepackage{lscape}
- \usepackage{array}
---

@@

# Task 1: Leaf sampling

@@

<!-- Participants: Dennis, Fabian, Louis, Lukas, Marie-Louise, Maxwell -->

@@

@@

@@

# Task 3 & 5: Leaf water content

# Appendix

\KOMAoptions{paper=portrait,pagesize} 
\recalctypearea
